---
title: "FLS 6415: Replication 4 - Instrumental Variables"
author: "Camila"
date: "15th April, 2020"
output: pdf_document
---


# FLS 6415: Replication 4 - Instrumental Variables

```{r message = F}
# open libraries
library(tidyverse)
library(plyr)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(knitr)
library(ggthemes)
library(Rmisc)
library(broom)
library(estimatr)
library(texreg)
library(AER)
```


First read the paper by Albertson and Lawrence (2009) on the course website.

The replication data is in the file IV.csv, and the important variables are described below. The rest of the variables in the data are just control variables for use in Q10. We are only going to replicate ‘Study 2’ of the paper (details from page 290), where the research question is whether watching a TV program on affirmative
action increased knowledge of and support for a proposition to eliminate affirmative action policies.


Watched_Program The respondent actually watched the TV program Encouraged_to_Watch The respondent was encouraged to watch the TV program during the phone call Info_Proposition The respondent’s self-assessment of whether they are well-informed about the Proposition

## 1. What is the treatment? What is the control? What is the outcome? What is the instrument for treatment?

 * Treatment: the participants in the treatment group were asked to watch the television broadcast. They were warned that they'd be interviewed about the program later, and received a letter and money as incentive.
 
 * Control: they were only warned that they'd be interviewed after the elections.
 
 * Outcome: Political attitudes.

 
```{r}
#open database
data <- "https://jonnyphillips.github.io/Methods_III/Classes/Class_6/Replication/IV.csv"
data_df <- read.csv(data)
```
 
 
## 2. If we did not know about instrumental variables, the basic observational regression we might run is to examine directly how the treatment variable is related to the outcome variable. Run this basic observational regression and interpret the results. NB: (The outcome variable is an ordered categorical variable - feel free to use either an ordered multinomial logit model or a simple linear OLS regression for all the questions, it doesn’t make much difference to the results).


```{r eval= F}

table(data_df$Info_Proposition)
reg1 <- data_df %>% 
 lm(Info_Proposition ~ Watched_Program, data = .) 

texreg(reg1, include.ci = F, digits = 3, caption = "Q1: Bivariate Regression")
```

```{r eval = F}
par(mfrow = c(2, 2))  # Split the plotting panel into a 2 x 2 grid
plot(reg1)  # Plot the model information
```

This model aims to estimate the treatment effect, having watched the program, on the dependent variable, "info proposition".

Being encouraged to watch explains 2,2% of the variation of info proposition. When someone is encouraged to watch, it increases by 0.296 point her info proposition level on average. It's statistically significant on the 0.001 level.


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept)      & $3.157^{***}$ \\
                 & $(0.043)$     \\
Watched\_Program & $0.296^{***}$ \\
                 & $(0.084)$     \\
\hline
R$^2$            & 0.024         \\
Adj. R$^2$       & 0.022         \\
Num. obs.        & 498           \\
RMSE             & 0.821         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q2: Bivariate Regression}
\label{table:coefficients}
\end{center}
\end{table}


## 3. Do you trust the treatment effect estimates from Q2? What are the major threats to causal inference here? Provide concrete examples of why the estimate in Q2 might be wrong.

I don't believe that having watched the program produced only this little effect on the info proposition. 

This is only a bivariate regression, it's like a t-test, it's not enough to assess the treatment effect in this research design.

Even though the individuals were randomly assigned to each group, it's important to include some control variables in the regression. Because of the fundamental problem of causal inference, we cannot put the same person in the treatment and control group at the same time.

Besides, we cannot guarantee that people that were randomly assigned to treatment paid attention to the program, even though they were warned about the interview content. So this person would have the same attitude in the control or in the treatment group. We could have the same kind of problem with people that would pay attention to the program,  even if they were not told about the content of the interview.

We need a regression model that enables us to assess the attitudes of people that really paid attention in the treatment group because they were asked to do it, and people who were in the control group and didn't pay attention to it.


## 4. To conduct an instrumental variables analysis, we first need to make sure we have a strong ‘first stage’, i.e. that our instrument predicts our treatment variable. Using a simple regression, what is the evidence about the strength of our first stage?

```{r eval = F}
table(data_df$Encouraged_to_Watch)
reg2 <- data_df %>% 
  lm( Watched_Program ~ Encouraged_to_Watch, data = .) 
texreg(reg2, include.ci = F, digits = 3, caption = "Q2: Bivariate Regression: Instrument and Treatment Variables")
```


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept)           & $0.044$       \\
                      & $(0.024)$     \\
Encouraged\_to\_Watch & $0.407^{***}$ \\
                      & $(0.034)$     \\
\hline
R$^2$                 & 0.220         \\
Adj. R$^2$            & 0.218         \\
Num. obs.             & 507           \\
RMSE                  & 0.384         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q4: Bivariate Regression: Instrument and Treatment Variables}
\label{table:coefficients}
\end{center}
\end{table}

Being watched the program explains 22% of the variation in the treatment. When someone is encouraged to watch increases 0.407 point on having watched. This coefficient is significant on the 0.001 level.

## 5. Now let’s perform the 2-Stage Least Squares instrumental variables methodology. First, save the fitted values of the first stage regression from Q4 as another column in your data.

```{r}
#data_df$yfit <- reg1$fitted.values
#error: Error in `$<-.data.frame`(`*tmp*`, yfit, value = c(`1` = 3.15675675675669, : replacement has 498 rows, data has 507
reg2 <- data_df %>% 
  lm( Watched_Program ~ Encouraged_to_Watch, data = .)
data_df <- data_df %>% 
  mutate(xfit = reg2$fitted.values)
```


## 6. Next, run the second-stage regression of the outcome variable on those fitted values from Q5. Carefully interpret the Instrumental Variables regression result.

```{r eval = F}
reg3 <- data_df %>% 
  lm(Info_Proposition ~ xfit, data = .)

texreg(reg3, include.ci = F, digits = 3, caption = "Q6: Bivariate Regression - y and ypredict")
```

This new model explains 1 % of the Info Proposition variation. The intercept is 3.173, which means that people have a bunch of information about the proposition before the election.

The independent variable, in this case, is the effect of having watched, taking into account that being encouraged has an effect on watching. In other terms, it's a having watched estimated with a bivariate regression model, in which, being encouraged is the independent variable.
When it varies in one level, the dependent variable increases 0.238, but it's not a statistically significant effect on 0.05 level.


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept) & $3.173^{***}$ \\
            & $(0.059)$     \\
xfit        & $0.238$       \\
            & $(0.183)$     \\
\hline
R$^2$       & 0.003         \\
Adj. R$^2$  & 0.001         \\
Num. obs.   & 498           \\
RMSE        & 0.830         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q6: Bivariate Regression - y and xfit}
\label{table:coefficients}
\end{center}
\end{table}


## 7. Conduct the equivalent all-in-one IV approach to the previous analysis using ivreg in the AER library in R or ivreg2 in Stata. Compare the result with the result from Q6.

```{r eval = F}
reg4 <- data_df %>% 
  AER::ivreg(Info_Proposition ~ Watched_Program|Encouraged_to_Watch, 
     data = .)

texreg(reg4, include.ci = F, digits = 3, caption = "Q7: Instrumental Regression")
```

The all-in-one approach estimates the Watched Program effect considering the effect of the Encouraged_to_watch instrumental variable, as the regressions before.

So we expect that they'll have similar regression outputs. 

The all-in-one regression explains 2.1% of the variation of the dependent variable. Both regressions have the same intercept. And coefficients very similar. As in the regression before, the effect of the Watched Program considering the effect of the Encouraged_to_watch instrumental variable is not significant on 0.05 level.


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept)      & $3.173^{***}$ \\
                 & $(0.058)$     \\
Watched\_Program & $0.232$       \\
                 & $(0.176)$     \\
\hline
R$^2$            & 0.023         \\
Adj. R$^2$       & 0.021         \\
Num. obs.        & 498           \\
RMSE             & 0.822         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q7: Instrumental Regression}
\label{table:coefficients}
\end{center}
\end{table}



## 8. A crucial assumption for the instrumental variables regression is the exclusion restriction: that the instrument ONLY affects the outcome through the treatment, and not through any other mechanism. We have to support this assumption by theory and supportive qualitative evidence as it cannot be empirically verified.
Make the argument that the encouragement to watch the program through the phone call ONLY affects participants’ information about the proposition through its effect on watching the program.

In this research design, the instrumental variable affects the outcome only through the treatment, because the instrumental variable is "being encouraged to watch" and the treatment variable is "watching the program". As only the treatment group received the incentive and the control group didn't, we can say that the instrumental variable only operates through the treatment.

## 9. Now pretend you are a reviewer/critic and make the argument that the exclusion restriction assumption is likely to be false.

Although only the treatment received the incentive to watch the program. This instrumental variable can affects the outcome through other mechanisms because a person who received the instrumental variable can feel more inclined to watch the program, but also to read the news or paying more attention to political issues. 

## 10. To what group of people (‘population’) does our estimate of the causal effect of treatment apply? How generalizable would our results be?

This experiment was conducted in Orange County, California. Thus, this study applies to the citizens of this city. Although the sample was randomly assigned we cannot generalize those results to all citizens in the world, because the population was the Orange County citizens, which is different from the citizens of other countries. We can generalize it to cities in California that are similar to this one.

## 11. The authors’ analysis in Table 4 is more complicated than ours only because it includes control variables in an attempt to make sure the instrument satisfies the exclusion restriction.

Add the control variables to both the first and second stage 2SLS methodology regressions and interpret the results (it may still be slightly different from the values in Table 4).

```{r eval = F}
##reg1 - First Stage
data_df_na <- data_df %>% 
  mutate(resid = Info_Proposition - yfit) %>% 
  na.omit(resi)
  
data_df_na$resid <-as.numeric(data_df_na$resid)


x <-data_df_na$resid
y <- data_df_na$Info_Proposition
yfit <- data_df_na$yfit
ggplot()+
  geom_point(aes(x=x, y))

cor(x, y)
cor(yfit, y)

ggplot()+
  geom_point(aes(x=yfit, y=y))

```



```{r eval = F}
##reg4 - Second Stage
data_df <- data_df %>% 
  mutate(yfit2 = reg4$coefficients * Watched_Program|Encouraged_to_Watch)

data_df_na <- data_df %>% 
  mutate(resid2 = Info_Proposition - yfit2) %>% 
  na.omit(resid2)
  
data_df_na$resid2 <-as.numeric(data_df_na$resid2)


x2 <-data_df_na$resid2
y <- data_df_na$Info_Proposition

plot(x2, y)
cor(x2, y)
```



```{r eval=F}
# First Stage
reg6 <- data_df %>% 
  lm(Info_Proposition ~ Watched_Program + partyid + pnintst + watchnat+ readnews + educad+ income+ gender + income + white, data = .)

texreg(reg6, include.ci = F, digits = 3, caption = "Q11: First Stage")
```

The first stage model explains 18.3% of the variation in the Info_Proposition. The intercept seems to be smaller than in the other regressions, but we cannot assure the difference is statistically significant. But it does tend to be smaller, as we add control variables.

When the variable Watched_Program varies in one unit, it increases 0.230 the Info_Proposition level, it's statistically significant on 0.05 level. 

The other control variables aren't statistically significant, the only exceptions are pnintst and readnews. The first increases in 0.262 points the dependent variable, the second in 0.112. They're statistically significant at 0.001. It's feasible because more informed and more interested in politics people tend to perform better on Info_Proposition.


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept)      & $1.801^{***}$ \\
                 & $(0.234)$     \\
Watched\_Program & $0.230^{**}$  \\
                 & $(0.077)$     \\
partyid          & $-0.017$      \\
                 & $(0.016)$     \\
pnintst          & $0.253^{***}$ \\
                 & $(0.047)$     \\
watchnat         & $0.000$       \\
                 & $(0.024)$     \\
readnews         & $0.109^{***}$ \\
                 & $(0.019)$     \\
educad           & $0.004$       \\
                 & $(0.013)$     \\
income           & $-0.009$      \\
                 & $(0.013)$     \\
gender           & $-0.053$      \\
                 & $(0.069)$     \\
white            & $0.065$       \\
                 & $(0.085)$     \\
\hline
R$^2$            & 0.207         \\
Adj. R$^2$       & 0.193         \\
Num. obs.        & 498           \\
RMSE             & 0.746         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q11: First Stage}
\label{table:coefficients}
\end{center}
\end{table}


```{r, eval=F}
# Second Stage
reg7 <- data_df %>% 
  ivreg(Info_Proposition ~ xfit + partyid + pnintst + watchnat+ readnews + educad+ income+ gender + income + white, data = .)

texreg(reg7, include.ci = F, digits = 3, caption = "Q11: Second Stage")

```

The second stage regression differently of the previous regression, considers the effect of the instrumental variable encouraged to watch on the independent variable encouraged to watch.

Differently from the Watched_Program alone, this new variable it's not statistically significant on 0.05 level because although the coefficients seem to be greater, the standard error also increases.


\begin{table}
\begin{center}
\begin{tabular}{l c }
\hline
 & Model 1 \\
\hline
(Intercept) & $1.719^{***}$ \\
            & $(0.243)$     \\
xfit        & $0.284$       \\
            & $(0.167)$     \\
partyid     & $-0.014$      \\
            & $(0.016)$     \\
pnintst     & $0.262^{***}$ \\
            & $(0.047)$     \\
watchnat    & $0.004$       \\
            & $(0.024)$     \\
readnews    & $0.112^{***}$ \\
            & $(0.019)$     \\
educad      & $0.003$       \\
            & $(0.013)$     \\
income      & $-0.010$      \\
            & $(0.013)$     \\
gender      & $-0.054$      \\
            & $(0.069)$     \\
white       & $0.060$       \\
            & $(0.086)$     \\
\hline
R$^2$       & 0.197         \\
Adj. R$^2$  & 0.183         \\
Num. obs.   & 498           \\
RMSE        & 0.751         \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Q11: Second Stage}
\label{table:coefficients}
\end{center}
\end{table}